Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-01-09 ms.tex
More modifications to the appendix.
Adding new versions of figures corresponding to cusp galaxies.

\newcommand{\Menc}{M_{\rm enc}}
\newcommand{\rhostar}{\rho_*}
\newcommand{\Mstar}{M_{\star}}
\newcommand{\Mseight}{M_{\star,8}}
\newcommand{\Mbh}[1][]{M_{\bullet#1}}
\newcommand{\Mbheight}{M_{\bullet,8}}
\newcommand{\MbheightExp}{\frac{\Mbh}{10^8 \Msun}}

@@

\begin{deluxetable}{lllllll}
\tabletypesize{\scriptsize}
\tabcolsep0.05in\footnotesize
\tablewidth{0pc}
\tablecaption{Cusp Results
\label{tab:sols}}
\tablehead{\colhead{$M_{\bullet,8}$} & \colhead{$v_{w,0}$} &
  \colhead{$\gamma$} & \colhead{$r_b$} &
  \colhead{$\dot{M}/\dot{M}_{\rm Edd}$} & \colhead{$t_{\rm
      cool}/t_{\rm ff} (r_s)$} & \colhead{comments}}
\startdata
0.01 & 300.0 & 0.8 & 100.0 & $ 3.2 \times 10^{ -4 }$ & 4.7 & rb in fact
unresolved \\
0.01 & 600.0 & 0.8 & 100.0 & $ 5.5 \times 10^{ -5 }$ & $ 3.2 \times
10^{ 2 }$ &  rb in fact unresolved\\
0.01 & 1200.0 & 0.8 & 100.0 & $ 9.4 \times 10^{ -6 }$ & $ 1.5 \times
10^{ 4 }$ &  rb in fact unresolved\\
0.1 & 300.0 & 0.8 & 100.0 & $ 2.5 \times 10^{ -3 }$ & 0.29 & energy
cons on outer grid \\
0.1 & 600.0 & 0.8 & 100.0 & $ 1.8 \times 10^{ -4 }$ & 97 &  \\
0.1 & 1200.0 & 0.8 & 100.0 & $ 3.1 \times 10^{ -5 }$ & $ 4.8 \times
10^{ 3 }$ &  energy cons on inner grid\\
1 & 300.0 & 0.8 & 100.0 & $ 1.6 \times 10^{ -2 }$ & $ 5.6 \times 10^{ -2 }$ &  \\
1 & 600.0 & 0.8 & 100.0 & $ 7.3 \times 10^{ -4 }$ & 21 &  \\
1 & 1200.0 & 0.8 & 100.0 & $ 9.9 \times 10^{ -5 }$ & $ 1.5 \times 10^{ 3 }$ &  \\
0.1 & 300.0 & 0.8 & 50.0 & $ 2.0 \times 10^{ -3 }$ & 0.46 &  \\
0.1 & 300.0 & 0.8 & 300.0 & $ 7.2 \times 10^{ -3 }$ & $ 6.7 \times 10^{ -2 }$ &  \\
0.1 & 300.0 & 0.8 & 200.0 & $ 5.3 \times 10^{ -3 }$ & 0.12 &  \\
0.1 & 300.0 & 0.8 & 400.0 & $ 8.9 \times 10^{ -3 }$ & $ 4.7 \times 10^{ -2 }$ &  \\
1 & 300.0 & 0.8 & 50.0 & $ 8.2 \times 10^{ -3 }$ & 0.19 &  \\
1 & 300.0 & 0.8 & 200.0 & $ 3.6 \times 10^{ -2 }$ & $ 1.7 \times 10^{ -2 }$ &  \\
1 & 300.0 & 0.8 & 300.0 & $ 5.2 \times 10^{ -2 }$ & $ 9.8 \times 10^{
  -3 }$ &  rb=400 pc was unsuccessful\\
\enddata
\end{deluxetable}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{profiles.eps}
  \caption{\label{fig:profiles}Radial profiles of the CNM density
    ({\it top}), temperature ({\it middle}), velocity ({\it bottom}),
    and interior X-ray luminosity ({\it bottom}) calculated for the
    cusp galaxies ($\Gamma=0.8$) within our grid.  Different colors
    denote different values of the effective wind heating rate,
    $\vwO=1200$ km s$^{-1}$ ({\it blue}), $\vwO$=600 km s$^{-1}$ ({\it
      orange}), and 300 km s$^{-1}$ ({\it green}).  Different
    linestyles correspond to different values of $\Mbh$, $\Mbh=10^6
    \Msun$ ({\it dot-dashed}), $\Mbh=10^7 \Msun$ ({\it solid}), and
    $\Mbh=10^8 \Msun$ ({\it dashed}). Squares mark out the location of
    the stagnation radius for each solution.
 }
\end{figure}

>>>>

\newcommand{\Menc}{M_{\rm enc}}
\newcommand{\rhostar}{\rho_*}
\newcommand{\Mstar}{m_{\star}}
\newcommand{\Mseight}{M_{\star,8}}
\newcommand{\Mbh}[1][]{M_{\bullet#1}}
\newcommand{\Mbheight}{M_{\bullet,8}}
\newcommand{\MbheightExp}{\frac{\Mbh}{10^8 \Msun}}

@@

\begin{deluxetable}{lllllll}
\tabletypesize{\scriptsize}
\tabcolsep0.05in\footnotesize
\tablewidth{0pc}
\tablecaption{Cusp Results
\label{tab:sols}}
\tablehead{\colhead{$M_{\bullet,8}$} & \colhead{$v_{w,0}$} &
  \colhead{$\gamma$} & \colhead{$r_b$} &
  \colhead{$\dot{M}/\dot{M}_{\rm Edd}$} & \colhead{$t_{\rm
      cool}/t_{\rm ff} (r_s)$} & \colhead{comments}}
\startdata
0.01 & 300.0 & 0.8 & 100.0 & $ 3.2 \times 10^{ -4 }$ & 4.7 & rb in fact
unresolved \\
0.01 & 600.0 & 0.8 & 100.0 & $ 5.5 \times 10^{ -5 }$ & $ 3.2 \times
10^{ 2 }$ &  rb in fact unresolved\\
0.01 & 1200.0 & 0.8 & 100.0 & $ 9.4 \times 10^{ -6 }$ & $ 1.5 \times
10^{ 4 }$ &  rb in fact unresolved\\
0.1 & 300.0 & 0.8 & 100.0 & $ 2.5 \times 10^{ -3 }$ & 0.29 & energy
cons on outer grid \\
0.1 & 600.0 & 0.8 & 100.0 & $ 1.8 \times 10^{ -4 }$ & 97 &  \\
0.1 & 1200.0 & 0.8 & 100.0 & $ 3.1 \times 10^{ -5 }$ & $ 4.8 \times
10^{ 3 }$ &  energy cons on inner grid\\
1 & 300.0 & 0.8 & 100.0 & $ 1.6 \times 10^{ -2 }$ & $ 5.6 \times 10^{ -2 }$ &  \\
1 & 600.0 & 0.8 & 100.0 & $ 7.3 \times 10^{ -4 }$ & 21 &  \\
1 & 1200.0 & 0.8 & 100.0 & $ 9.9 \times 10^{ -5 }$ & $ 1.5 \times 10^{ 3 }$ &  \\
0.1 & 300.0 & 0.8 & 50.0 & $ 2.0 \times 10^{ -3 }$ & 0.46 &  \\
0.1 & 300.0 & 0.8 & 300.0 & $ 7.2 \times 10^{ -3 }$ & $ 6.7 \times 10^{ -2 }$ &  \\
0.1 & 300.0 & 0.8 & 200.0 & $ 5.3 \times 10^{ -3 }$ & 0.12 &  \\
0.1 & 300.0 & 0.8 & 400.0 & $ 8.9 \times 10^{ -3 }$ & $ 4.7 \times 10^{ -2 }$ &  \\
1 & 300.0 & 0.8 & 50.0 & $ 8.2 \times 10^{ -3 }$ & 0.19 &  \\
1 & 300.0 & 0.8 & 200.0 & $ 3.6 \times 10^{ -2 }$ & $ 1.7 \times 10^{
  -2 }$ &  possible issue w/ conv \\
1 & 300.0 & 0.8 & 300.0 & $ 5.2 \times 10^{ -2 }$ & $ 9.8 \times 10^{
  -3 }$ &  possible issue w/ conv ; rb=400 pc was unsuccessful\\
\enddata
\end{deluxetable}

\begin{table*}
\centering
\begin{minipage}{18cm}
\caption{Models Evolved and Outflow
Properties\label{t:models}\label{t:results}. The first
six columns show model name, HMNS lifetime, stellar period, fractional
radial resolution
at inner boundary, and irradiation by the neutron star, respectively.
The last eight columns show integrated properties of the outflow,
restricted to equatorial
 ($\theta \in [30^\circ,150^\circ]$) and polar ($\theta<30^\circ$ and
$\theta > 150^\circ$)
latitudes. Each group of four columns includes the mass-flux weighted
electron fraction, entropy,
and expansion time at a radius where the mass-flux weighted temperature is
$5\times10^9$~K, as
well as the net mass in unbound material crossing a surface at $10^9$~cm,
normalized
by the initial torus mass.}
\begin{tabular}{lccccccccccccc}
\hline
{Model}&
{$t_{\rm ns}$} &
{$P_\star$} &
{$\alpha$} &
{$\Delta r_{\rm min}/R_\star$} &
{$\star$-Irr.} &
\multicolumn{4}{c}{Equatorial Outflow} &
\multicolumn{4}{c}{Polar Outflow$^b$}\\
{ } & \multicolumn{2}{c}{(ms)} &  {}  &  {}  & {} &
{$\bar{Y}_e$} &
{$\bar{s}$ } &
{$t_{\rm exp}$} &
{$M_{\rm ej,unb}/M_{\rm t0}$} &
{$\bar{Y}_e$} &
{$\bar{s}$ } &
{$t_{\rm exp}$} &
{$M_{\rm ej,unb}/M_{\rm t0}$}\\
\multicolumn{6}{c}{} & {} & {($k$/b)} & {(ms)} & {(\%)} & {} & {($k$/b)} &
{(ms)} & {(\%)}\\
%}
\hline
t000A3      & 0        & ... & 0.03 & 5E-3 & No   & 0.18 & 18 & 27  & 2.1
& ...  & ... & ... & 0.9 \\
t010A3p15   & 10       & 1.5 &      &      & Yes  & 0.19 & 20 & 30  & 2.5
& ...  & ... & ... & 1.0 \\
t030A3p15   & 30       &     &      &      &      & 0.23 & 21 & 27  & 3.9
& 0.50 & 45  & 7.6 & 1.3 \\
t100A3p15   & 100      &     &      &      &      & 0.28 & 20 & 33  & 9.2
& 0.47 & 42  & 11  & 4.0 \\
t300A3p15   & 300      &     &      &      &      & 0.30 & 20 & 32  & 28
& 0.44 & 38  & 17  & 8.8 \\
tInfA3p15   & $\infty$ &     &      &      &      & 0.32 & 21 & 42  & 67
& 0.43 & 52  & 17  & 22  \\
\noalign{\smallskip}
pA1p15      & $\infty$ & 1.5 & 0.01 & 5E-3 & Yes  & 0.36 & 21 & 61  & 47
& 0.45 & 52  & 19  & 22 \\
pA3p20      &          & 2   & 0.03 &      &      & 0.30 & 29 & 37  & 62
& 0.37 & 62  & 15  & 17 \\
pA3p15xs    &          & 1.5 &      &      & No   & 0.27 & 21 & 45  & 56
& 0.35 & 61  & 15  & 23 \\
\noalign{\smallskip}
rA3p15r1    & $\infty$ & 1.5 & 0.03 & 1E-2 & Yes  & 0.32 & 21 & 45  & 69
& 0.43 & 53  & 17  & 22 \\
rA3p15r2$^a$   &       &     &      & 2E-3 &      & ... & ... & ... & ...
& ...  & ... & ... & ... \\
\hline
\hline
\multicolumn{14}{l}{$^a$ Model rA3p15r2 was evolved for a shorter time.
See Appendix~\ref{s:neutrino_details}
                    for details.}\\
\multicolumn{14}{l}{$^b$ Average thermodynamic quantities are not computed
if there is no region
                         where the average temperature is $\sim 5\times 10^9$~K.}
\label{table:models}
\end{tabular}
\end{minipage}
\end{table*}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{profiles.eps}
  \caption{\label{fig:profiles}Radial profiles of the CNM density
    ({\it top}), temperature ({\it middle}), velocity ({\it bottom}),
    and interior X-ray luminosity ({\it bottom}) calculated for the
    cusp galaxies ($\Gamma=0.8$) within our grid.  Different colors
    denote different values of the effective wind heating rate,
    $\vwO=1200$ km s$^{-1}$ ({\it blue}), $\vwO$=600 km s$^{-1}$ ({\it
      orange}), and 300 km s$^{-1}$ ({\it green}).  Different
    linestyles correspond to different values of $\Mbh$, $\Mbh=10^6
    \Msun$ ({\it dot-dashed}), $\Mbh=10^7 \Msun$ ({\it solid}), and
    $\Mbh=10^8 \Msun$ ({\it dashed}). Thin lines correspond to cusp
    galaxies ($\gamma$=0.8) and thick lines correspond to core
    galaxies ($gamma$=0.1). Squares mark out the location of
    the stagnation radius for each solution.
 }
\end{figure}
